\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[top=1cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

% Setup font
\usepackage{fontspec}
\setmainfont{Arial}

% Adjust section spacing
\titlespacing\section{0pt}{5pt plus 1pt minus 1pt}{5pt plus 1pt minus 1pt}
\titlespacing\subsection{0pt}{5pt plus 1pt minus 1pt}{5pt plus 1pt minus 1pt}

% Color for headers
\titleformat{\section}{\large\bfseries\color{blue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{black}}{}{0em}{}

% Start of Document
\begin{document}

% Header
\noindent
\begin{minipage}[t]{0.65\textwidth}
    {\LARGE \textbf{MRIDUL PANDEY}} \\
    4th year Undergraduate, Indian Institute of Technology Kanpur \\
    Major in Electrical Engineering \\
    Minor in Computer Science \& Engineering (Algorithms)
\end{minipage}
\begin{minipage}[t]{0.35\textwidth}
    \flushright
    \href{mailto:mridul21@iitk.ac.in}{mridul21@iitk.ac.in} \\
    \href{https://github.com/MridulPandey17}{github.com/MridulPandey17} \\
    +91 971 740 1684 \\
    Kanpur, India
\end{minipage}

\vspace{2mm} % Horizontal rule
\hrule
\vspace{2mm}

% Education
\section*{EDUCATION}
\noindent
\textbf{Indian Institute of Technology Kanpur (IIT Kanpur)} \hfill \textbf{Aug 2021 -- Present} \\
B.Tech in Electrical Engineering \hfill \textbf{CPI: 9.47/10} \\
\textit{Minor: Computer Science \& Engineering (Algorithms)} \\
\vspace{2mm}

\textbf{Amity International School Pushp Vihar, New Delhi} \hfill \textbf{2019 -- 2021} \\
Senior Secondary (XII), CBSE \hfill \textbf{Percentage: 97.4\%} \\
\vspace{2mm}

\textbf{Amity International School Pushp Vihar, New Delhi} \hfill \textbf{2017 -- 2019} \\
Secondary (X), CBSE \hfill \textbf{Percentage: 95.4\%}

% Key Achievements
\section*{KEY ACHIEVEMENTS}
\begin{itemize}[left=0pt]
    \item Received Academic Excellence Award for exceptional academic performance in 2021-22, 2022-23.
    \item Secured global rank 2 in MADAR3.2N, conducted by ASRU, building Biophil in Bengali ASR models.
    \item Secured rank 1 in all over India in BCG Ideathon 2023, for EV charging stations.
    \item Secured All India Rank 1015 in JEE Advanced 2021.
    \item Secured All India Rank 206 in JEE Mains 2021.
    \item Coderforces rating: 1631; Handle: ElectroNova.
    \item Secured global rank 432 in Codeforces Round 966.
\end{itemize}

% Courses
\section*{COURSES}
\noindent
Data Structures \& Algorithms, Algorithms 2, Probability \& Statistics, Intro to Machine Learning, Embedded \& Cyber-Physical Systems, Linear Algebra \& Differential Equations, Industrial Internet of Things (IIoT)

% Technical Skills
\section*{TECHNICAL SKILLS}
\noindent
\textbf{Programming Languages:} C++, C, Python \\
\textbf{ML Frameworks \& Libraries:} PyTorch, OpenAI, Sklearn, TensorFlow, HuggingFace Transformers \\
\textbf{Utilities:} Git, Matplotlib, seaborn, TEx, QGIS

% Work Experience
\section*{WORK EXPERIENCE}
\noindent
\textbf{Tourism and Investment Promotion in Rajasthan} \hfill \textit{May 2024 -- Jul 2024} \\
\textbf{Summer Associate | Boston Consulting Group} \\
- Identified key sectors to improve tourism in Rajasthan, focusing on increasing tourism connectivity.\\
- Analysed Air \& Rail connectivity of famous tourist places of Rajasthan using QGIS, identifying required infrastructure. \\
- Identified key private partnerships for Rajasthan across 9 buckets to promote tourism. \\
\vspace{2mm}

\noindent
\textbf{Automating Nurse-patient Interaction using Generative AI} \hfill \textit{Dec 2023 -- May 2024} \\
\textbf{ML Intern | Noora Health Organization} \\
- Digitalized patient reports by implementing few-shot learning chain of thought with Google’s Vertex AI. Achieved 85\% accuracy. \\
- Built a multilingual query retrieval RAG model for maternal care, answering medical queries. \\
- Implemented the RAG model using OpenAI, improving response accuracy.

% Key Projects
\section*{KEY PROJECTS}
\noindent
\textbf{ASR for Hindi Language | Madhav Lab, IIT Kanpur} \hfill \textit{July 2023 -- Jul 2024} \\
- Built a Conformer model for Hindi ASR equipped with greedy CTC decoder, beam search \& KenLM obtaining a WER of 11.8\% \& CER of 7\%. \\
- Improved ASR module accuracy to 7.9\% WER, 6.9\% CER using fine-tuned Wav2Vec pre-trained on English ASR. \\
\vspace{2mm}

\noindent
\textbf{Low Cost PM2.5 Sensor Calibration | National Aerosol Facility, IIT Kanpur} \hfill \textit{May 2023 -- Apr 2024} \\
- Calibrated low-cost PM2.5 sensors in Bihar and UP using a novel Self-Supervised Learning algorithm. \\
- Designed a dashboard using Figma to represent PM2.5 sensor data. \\
\vspace{2mm}

\noindent
\textbf{Failure Forecasting for Low Cost Sensors | National Aerosol Facility, IIT Kanpur} \hfill \textit{Dec 2022 -- Apr 2023} \\
- Developed a novel model using LSTM and Deep Forecasting techniques.

% Positions of Responsibility
\section*{POSITIONS OF RESPONSIBILITY}
\noindent
\textbf{Leader | IITK Consulting Group} \hfill \textit{May 2023 -- Apr 2024} \\
- Led the team in working with startup organizations promoting geospatial data applications. \\
\vspace{2mm}

% Footer or additional sections like references can go here if needed

\end{document}
